### 2020-03-12 paper/main.tex
deleting code files

[ What is raw signal and discrete, compare them, ]

\chapter{Preprocessing}
We compared this method to other features extracted from Fourier-transform, Short Time Fourier transform, sliding window method, and polar coordinates taken directly from the signals amplitude/phase value.

@@

We use spline interpolation in order to resize each level of decomposition into a single array.

\section{Models}
[introduce models definitions]
[EXPLAIN LOSS AND HOW ACCURACY IS MEASURED]

This section gives an overview of the theoretical background of concepts discussed in this work.

@@

[cnn]

@@

@@

@@

@@

Our CNN has an architecture consisting of 3 convolutional layers each followed by a batch normalization and dropout layer then finally connected to two dense layers (Figure X). We found no improvements in performance when we attempted to make it deeper by adding additional convolutional layers as well as skip connections.

\subsection{LSTM}
We wanted to keep our LSTM network as small as possible, for X purposes, so we went with two LSTM layers of 128 hidden states and a dropout rate of 4/10  followed by a dense layer of 128 connections. We attempted different state sizes but found 128 to be the smallest number with the best consistent performance.

We propose a multimodal learning architecture for the purpose of time series classification which is illustrated in Figure (X). The multimodal architecture allows our data to vary in size and given that all four levels of decomposition have varying length due to downsampling, we propose each model to learn the representation of each distinct feature. For this architecture we propose two models, a 1D CNN and an LSTM, in which we employ two CNN’s and 1 LSTM. They are all concatenated after their respective dense layer which performs the final   We tried numerous variations and saw no impact on performance.

@@

In order to classify those images we created a CNN for it specifically and avoided using our existing CNN in order to make it deeper and increase performance when images aren’t that classifiable. We explored several architectures, such as, ResNet, Inception-v4, and AlexNet but we decided to create an architecture similar to AlexNet due to the variation and size of datasets we used we couldn’t create a model deeper or more complex than it otherwise performance would drop because we didn’t have enough data to properly train it. We were able to achieve 60\% accuracy on our dataset.

@@

\chapter{Markov Transition Fields}
% We propose a framework similar to [] for encoding dynamical transition statistics,
% but we continue their work by considering ith order Markov transition probabilities.
% Given a time series X, we decompose its magnitude axis into two separate
% properties by representing it as a polar coordinate, Xangular and Xradial. We then
% identify the Q quantile bins for both properties and the temporal values Xtime
% and assign each x ∈ Xangular, Xradial, Xtime to its corresponding bin qj (j in
% [1, Q]). Thus we construct three QxQ adjacency transition matrices, Wangular,
% Wradial, Wtime, by counting transitions among quantile bins in the manner of a
% ith order Markov chain along the time axis.

% W does not take into account the temporal axis so to prevent any information
% loss we construct a Markov Transition Field (MTF) for each W. The MTF
% denotes the probability of transitioning from qi to qj for each x ∈ X. This,
% in turn, allows us to consider the transition probability on the magnitude and
% temporal axis.

% As described in [] the MTF encodes the multi-span transition probabilities
% of the time series, but given that we have three different M’s we modify their
% approach and consider each M to be a separate color channel of RGB where
% Mangular is red, Mtime is blue, Mradial is green. We perform linear interpolation
% on each M individually to extend the probabilities to be within the range of 0 and 255.

>>>>

[ What is raw signal and discrete, compare them, ]
[explain hv, vv]
\chapter{Preprocessing}
We compared this method to other features extracted from Fourier-transform, Short Time Fourier transform, sliding window method, and polar coordinates taken directly from the signals amplitude/phase value.

@@

We use spline interpolation in order to resize each level of decomposition into a single array. We tested different sizes of interpolation from N to N/3 where N is the size of the largest discrete signal size and found no drop in performance.

\subsection{Each level}
Figure {X} depicts our model in which each level of decomposition is treated as its own dataset. We found no difference in accuracy compared to the resampling method.

\chapter{Models}
[introduce models definitions]
[EXPLAIN LOSS AND HOW ACCURACY IS MEASURED]

\section{Definition}
This section gives an overview of the theoretical background of concepts discussed in this work.

@@

\subsection{CNN}
[cnn]

@@

\subsection{LSTM}

@@

\subsection{multimodal}

@@

\section{Architectures Used}

@@

Our CNN architecture consists of 3 convolutional layers each followed by a batch normalization and dropout layer then finally connected to two dense layers (Figure X). We attempted to make it deeper but found inconsistent performance across all of our datasets.
[add figure]
\subsection{LSTM}
We wanted to keep our LSTM network as small as possible, for X purposes, so we went with two LSTM layers of 128 hidden states and a dropout rate of 4/10  followed by a dense layer of 128 connections. We attempted different state sizes but found 128 to be the smallest number with the best consistent performance.

[add figure]

\subsection{Final method}
We propose a multimodal learning architecture for the purpose of time series classification which is illustrated in Figure (X). The multimodal architecture allows our data to vary in size and given that all four levels of decomposition have varying length due to downsampling, we propose each model to learn the representation of each distinct feature. For this architecture we propose two models, a 1D CNN and an LSTM, in which we employ two CNN’s and 1 LSTM. They are all concatenated after their respective dense layer which performs the final   We tried numerous variations and saw no impact on performance. 
[add figure]

@@

In order to classify those images we created a CNN for it specifically and avoided using our existing CNN in order to make it deeper and increase performance when images aren’t that classifiable. We explored several architectures, such as, ResNet, Inception-v4, and AlexNet but we decided to create an architecture similar to AlexNet due to the variation and size of datasets we used we couldn’t create a model deeper or more complex than it otherwise performance would drop because we didn’t have enough data to properly train it.

\subsection{mtf}
We approach our MTF is slightly different than [] because instead of performing it over all samples in the dataset we perform it for every signal. The three attributes we use are values o

@@

\chapter{Markov Transition Fields}
We propose a framework similar to [] for encoding dynamical transition statistics,
but we continue their work by considering ith order Markov transition probabilities.
Given a time series X, we decompose its magnitude axis into two separate
properties by representing it as a polar coordinate, Xangular and Xradial. We then
identify the Q quantile bins for both properties and the temporal values Xtime
and assign each x in Xangular, Xradial, Xtime to its corresponding bin qj (j in
[1, Q]). Thus we construct three QxQ adjacency transition matrices, Wangular,
Wradial, Wtime, by counting transitions among quantile bins in the manner of a
ith order Markov chain along the time axis.

W does not take into account the temporal axis so to prevent any information
loss we construct a Markov Transition Field (MTF) for each W. The MTF
denotes the probability of transitioning from qi to qj for each x in X. This,
in turn, allows us to consider the transition probability on the magnitude and
temporal axis.

As described in [] the MTF encodes the multi-span transition probabilities
of the time series, but given that we have three different M’s we modify their
approach and consider each M to be a separate color channel of RGB where
Mangular is red, Mtime is blue, Mradial is green. We perform linear interpolation
on each M individually to extend the probabilities to be within the range of 0 and 255.

\section{}
